### 2020-04-22 intro.tex
high-level

From a realiability perspective, Titan was a very interesting
machine. Its operation was forced to execute three very significant
rework cycles, two on the mechanical assembly affecting the PCIe
connector from the GPU daughtercard to the motherboard, and a
replacement of about 11,000 GPU assemblies because of a failing
resistor on a printed circuit board. We write primarily about the epoch
that includes this last rework cycle. This includes Titan's most
stable and failure free period and contains the most reliable data on
GPU operation.

\begin{figure*}[tb]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{Volume of GPU swaps detected on Titan at inventories. Our
    analysis begins with units in place by 2014. A break-in period
    before 2014 involved working out mechanical assembly issues at
    PCIe connectors.}
  \label{fig:chronology}
\end{figure*}
Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles and stable periods as indicated by the number of GPU changes at
periodic inventories.  The first two rework cycles before 2014 can be
characterized as a break-in period on a new system that is first of
its kind and pushes many technological boundaries, in this case mainly
regarding blade mechanical assembly. The resulting field engineering
and data collection changes generated high GPU swap counts before
2014. Late 2013 begins a very long period of high reliability and
stable operation with very few issues until about mid 2016, when GPU
failures begin to rise. This results in the final rework cycle,
replacing 11,000 GPUs throughout much of 2017. The peak at the end in
the figure is an artifact of turning off or ``removing'' all the
units.

@@

Our analysis focuses on GPU boards that were installed in the second
rework cycle and later, essentially units installed near the beginning
of 2014 and later. We will make the data as well as our analysis codes
producing the graphics available in a public repository (see,
\cite[repository]{repositoryreference}).  While the data is only a 7 MB
file, due to the size of Titan it represents over 100,000 years of GPU
operation and may be the largest publicly available GPU reliability
data set. Our hope is that others will use it for reliability research
and go beyond the results presented here.

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the
data cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A time between failures (TBF) analysis
is given in Sec.~\ref{section:tbf}. Survival analysis based on
Kaplan-Meier modeling (KM) and Cox regression modeling (CR) of
relative hazard rates in various locations are in
Sec.~\ref{section:survival}. Finally, we discuss our main conclusions
and recommendations in Sec.~\ref{section:discussion}.

>>>>

From a realiability perspective, Titan was a very interesting
machine. Its operation was forced to execute three very significant
rework cycles, two on the mechanical assembly affecting the PCIe
connector from the GPU daughtercard to the motherboard, and one to
replace about 11,000 GPU assemblies because of a failing resistor on
their printed circuit board. We write primarily about the GPU
operation epoch that includes this last rework cycle. This epoch of
nearly 6 years includes Titan's most stable and failure free period
and contains the most reliable data on GPU operation.

\begin{figure*}[tb]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{Volume of GPU swaps detected on Titan at inventories. Our
    analysis begins with units in place by 2014. A break-in period
    before 2014 involved working out mechanical assembly issues at
    PCIe connectors.}
  \label{fig:chronology}
\end{figure*}
Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles and stable periods as indicated by the number of GPU changes at
periodic inventories.  The first two rework cycles before 2014
involving blade mechanical assembly can be characterized as a break-in
period on a new system that is first of its kind and pushes many
technological boundaries. The resulting field engineering as well as
data collection changes are responsible for the high GPU swap counts
before 2014. Late 2013 begins a very long period of high reliability
and stable operation with very few issues until about mid 2016, when
GPU failures begin to rise. This results in the final rework cycle,
replacing 11,000 GPUs throughout much of 2017. The peak at the end in
the figure is an artifact of turning off or ``removing'' all the
units as Titan is shut down and disassembled.

@@

Our analysis focuses on GPU boards that were installed in the second
rework cycle and later, essentially units installed near the beginning
of 2014 and later. Figure~\ref{fig:chronology} is the only one
involving data prior to 2014. All analyses and figures that follow use
only data from 2014 onward. We make the data as well as our analysis
codes to reproduce the graphics available in a public repository (see,
\cite[repository]{repositoryreference}).  While the data is only a 7
MB file, due to the size of Titan it represents over 100,000 years of
GPU operation and may be the largest publicly available GPU
reliability data set. Our hope is that others will use it for
reliability and survival analysis research and go beyond the results
presented here.

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the
data cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A time between failures (TBF) analysis
is given in Sec.~\ref{section:tbf}. Survival analysis based on
Kaplan-Meier modeling (KM) and Cox regression modeling (CR) of
relative hazard rates in various locations are in
Sec.~\ref{section:survival}. A high-level difference between a TBF
analysis and survival analysis (SA) is that TBF studies largely how
GPU reliability affects the machine, wheras SA studies largely how the
machine affects GPU reliability.  Finally, we discuss our main
conclusions and recommendations in Sec.~\ref{section:discussion}.
